### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

1. [Chicago neighborhoods geojson](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson) - part of [a great collection](https://github.com/blackmad/neighborhoods/) by [@blackmad](https://github.com/blackmad).
We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushed data files under "notebooks" to the target render directory.
This will allow us to consume the file from the browser for data visualizations.

@@

We wish to plot our trips as line segments
(Vega-Lite [Rule](https://vega.github.io/vega-lite/docs/rule.html)s)
over a map.

>>>>

1. [Chicago neighborhoods geojson](https://github.com/blackmad/neighborhoods/blob/master/chicago.geojson) - part of [a great collection](https://github.com/blackmad/neighborhoods/) by [@blackmad](https://github.com/blackmad).
We keep this file under "notebooks/data/". By default, [Clay](https://scicloj.github.io/clay) pushes data files under "notebooks" to the target render directory.
This will allow us to consume the file from the browser for data visualizations.

@@

We wish to plot our trips as line segments
(Vega-Lite [Rules](https://vega.github.io/vega-lite/docs/rule.html))
over a map.
